\documentclass[a4paper, oneside, article]{memoir}

\usepackage[T1]{fontenc}

% Handle references with nicely with \cref
\usepackage{hyperref}
\hypersetup{linkcolor=black, colorlinks=true, urlcolor=black}
\usepackage{cleveref}

% Palatino is a nice font.
\usepackage[sc]{mathpazo}

\usepackage[top=1.0in, bottom=1in, left=1.5in, right=1.5in]{geometry}

% Auto-space after \emph{cake}
\usepackage{xspace}

% List continuation counter 'to be continued'
\newcounter{tbc}

\begin{document}
\thispagestyle{empty} % No page number on first page
\begin{center}
  \textsc{\huge Clearhaus Ceremonial Cake Legislation}
  \\
  {\footnotesize \href{https://semver.org/}{Version 0.4}}
\end{center}

\chapter{Legislative basics}

\begin{enumerate}[ยง 1]
  \item This legislation applies to all employees of Clearhaus, Quickpay, and 3dsecure.io.


  \item The term \emph{Cake} as used in this document may be
    interpreted in a literal sense --- i.e.\ cake --- as well as pastry, ice
    cream, etc.

  \item Individuals having undergone/undergoing any described circumstance are
    referred to as \emph{cake offering responsible} (\emph{COR}).

  \item Foodstuff not containing an appropriate amount of sugar, or with an
    unacceptably low amount of calories, may not be interpreted as
    \emph{cake}.

    Upon the judgement that \emph{cake} is not an acceptable term for the
    offering, \emph{COR} will be obligated to procure proper \emph{cake}.

  \item \Cref{chp:circumstances} describes circumstances in which a traditional
    offering of \emph{cake} is expected by the \emph{COR}. Notice that
    \textbf{ยง13} is an exception.
    
  \item the amount of \emph{cake} should at least serve 50 people, ensuring that at least a couple of persons from each department gets a piece.


  % Save which enum we are on
  \setcounter{tbc}{\value{enumi}}
\end{enumerate}

\chapter{Cake invoking circumstances}\label{chp:circumstances}
\begin{enumerate}[ยง 1]
  % Restore enumerator count
  \setcounter{enumi}{\value{tbc}}

  \item Birthday
  \item Wedding
  \item New car
  \item Impregnation of any other individual (by \emph{COR}) or impregnation of
    \emph{COR}.
  \item Using incorrect recipient in sufficiently important email.
  \item Having passed an exam, either final exam or getting the top grade.
  \item Extreme weather\footnote{DMI Category 2 Warning in the Aarhus area.} (\emph{cake responsible organization} is Clearhaus A/S).
  \item Winning a programming competition.
  \item Returning from parental leave.
  \item Going from student position, internship or similar non-full-time-employment to full-time employment in Clearhaus, Quickpay, or 3dsecure.io.
  \item Appearance by photo or text in ISBN-numbered publication.
  \item Activating the fire/burglar alarm.
  \item Shameful defeat (0--7) in foosball.
  \item Shameful defeat (0--6) in padel.
  \item Shameful defeat (0--11) in table tennis.
  \item Code deployment causing service outage.
  \item Forgetting that you are on call.
  \item Being made (partially) superfluous by automation.
  \item Loosing office key fob.
  \item Occupying a meeting room booked by another person (without leaving immediately)
\end{enumerate}
\end{document}
